%-------------------------
% Rover Resume Template
% Link: https://github.com/subidit/rover-resume
%------------------------

\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{inter} % https://tug.org/FontCatalogue/
\renewcommand*\familydefault{\sfdefault}

\usepackage{geometry}
\geometry{
a4paper,
top=1.8cm,
bottom=1in,
left=2.5cm,
right=2.5cm
}

\setcounter{secnumdepth}{0} % remove section numbering
\pdfgentounicode=1 % make ATS friendly

% \usepackage[dvipsnames, svgnames, x11names]{xcolor} 
\usepackage[dvipsnames]{xcolor} % xcolor.pdf Sec.4 Colors by Name
\colorlet{icnclr}{gray}
% \colorlet [⟨type⟩]{⟨name⟩}[⟨num model⟩]{⟨color ⟩}
% \definecolor[⟨type⟩]{⟨name⟩}{⟨model-list⟩}{⟨spec-list⟩}

\usepackage{enumitem}
\setlist[itemize]{
    noitemsep,
    left=0pt..1.5em
}
\setlist[description]{itemsep=0pt}
\setlist[enumerate]{align=left}

\usepackage{titlesec}
% \titlespacing{command}{left spacing}{before spacing}{after spacing}[right]
% \titlespacing{\section}{0pt}{*3}{*1}
\titlespacing{\subsection}{0pt}{*0}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
% \titleformat{<command>}[<shape>]{<format>}{<label>}{<sec>}{<before-code>}[<after-code>]  
\titleformat{\section}{\color{Sepia}\large\fontseries{black}\selectfont\uppercase}{}{}{\ruleafter}[\global\RemVStrue]
\titleformat{\subsection}{\large\fontseries{semibold}\selectfont}{}{}{\rvs}
\titleformat{\subsubsection}{\large\fontseries{medium}\selectfont}{}{}{}

\usepackage{xhfill} 
\newcommand\ruleafter[1]{#1~\xrfill[.5ex]{1pt}[gray]} % add rule after title in .5 x-height 

\newif\ifRemVS % remove vspace between \section & \subsection
\newcommand{\rvs}{
    \ifRemVS
        \vspace{-1.5ex}
    \fi
    \global\RemVSfalse
}


\usepackage{fontawesome5}

\usepackage[bookmarks=false]{hyperref} % [imp!]
\hypersetup{ % https://en.wikibooks.org/wiki/LaTeX/Hyperlinks
    colorlinks=true,
    urlcolor=Sepia,
    pdftitle={Luqmanul Hakim - Resume},
}

\usepackage[page]{totalcount}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}	
\fancyhf{}							
\cfoot{\color{darkgray} Luqmanul Hakim Resume -- Page \thepage{} of \totalpages}


\begin{document}

%== HEADER ==%
\begin{center}
    {\fontsize{36}{36}\selectfont \interheavy Luqmanul Hakim} \\ \bigskip
    {\color{gray}\fontsize{13}{13}\selectfont Software Engineer with DevOps Mindset with 6+ year experiences} \\ \bigskip
    {\color{icnclr}\faEnvelope[regular]} \href{mailto:luqmanulhacim@outlook.com}{luqmanulhacim@outlook.com} $|$
    {\color{icnclr}\faIcon{mobile-alt}} \href{tel:+6287788531313}{+62 877 8853 1313}
    \\ {\color{icnclr}\faLinkedinIn} \href{https://www.linkedin.com/in/luqmanulhakim5}{linkedin.com/in/luqmanulhakim5} $|$
    {\color{icnclr}\faGithub} \href{https://github.com/orgmatileg}{github.com/orgmatileg}
\end{center}

\section{Professional Summary}
 {Engineering manager and software engineer with demonstrated experience in developing software with
  values across different industries, starting from SMEs, startups, until unicorn companies. With my unique
  style of leadership, devops, and product mindset, I am able to build and empower several tech teams in
  various companies while being passionate about business strategy and driving innovation through
  technology, even though I only have a high school diploma degree.}
%===============


\section{Experience}
%===================
\subsection{Mejadokter - Health Tech}
\subsubsection{Technical Founder | Jan 2020 - Now \hfill Bali, Remote}
\begin{itemize}
    \item \textbf{Mission:} Spearheaded Mejadokter's mission to revolutionize healthcare operations by digitizing medical data and clinical management systems. Led the technology strategy and development, delivering robust digital solutions that enhanced operational efficiency and client satisfaction.
    \item \textbf{Tech Stack:} Node.js, Nest.js, Express.js, Go, MongoDB, Redis, React, Kafka, AWS.
    \item \textbf{Key Achievements:}
    \begin{itemize}
        \item \textbf{Data Migration Tool:} Developed and deployed a scalable data migration tool, enabling health facilities to transition seamlessly from multiple clinic management systems to Mejadokter. Reduced onboarding time by 40\% and improved data accuracy by 25\%.
        \item \textbf{Product Development:} Led a cross-functional team in building and launching Mejadokter's core products, empowering 50+ clinics to enhance service delivery, patient care, and staff productivity.
        \item \textbf{Strategic Integrations:} Designed and executed a technology roadmap, integrating critical systems such as SatuSehat, BPJS Antrian Online (JKN), BPJS Pcare.
        \item \textbf{Marketing \& CRM Solutions:} Developed tailored Marketing and CRM solutions for clinics, increasing patient engagement by 30\% and retention rates by 20\%.
        \item \textbf{Website Builder:} Designed and launched an intuitive website builder for clinics, boosting online presence and patient interaction, resulting in a 35\% increase in patient inquiries.
        \item \textbf{Infrastructure Development:} Built Mejadokter's infrastructure from scratch, ensuring scalability, reliability, and high availability to support business growth and user demands.
    \end{itemize}
\end{itemize}

\subsection{TradersFamily.id - Trading Forex}
\subsubsection{DevOps Engineer | Jul 2024 - Present \hfill Jakarta, Remote (Part-time, Contract end soon)}
\begin{itemize}
    \item \textbf{Mission:} 
    \begin{itemize}
        \item Spearheaded the adoption of DevOps practices and tools (Jenkins, Terraform, Docker, Docker Swarm) to streamline development workflows and improve team efficiency.
        \item Delivered significant infrastructure improvements and cost optimizations, resulting in enhanced system reliability and reduced operational expenses.
    \end{itemize}
    \item \textbf{Tech Stack:} Jenkins, Terraform, Docker, Docker Swarm, Loki, Grafana, Prometheus, Node-Exporter, cAdvisor, HAProxy, MariaDB Galera Cluster, AWS, WordPress.
    \item \textbf{Key Achievements:}
    \begin{itemize}
        \item \textbf{Infrastructure Automation:} Built Docker Swarm and Jenkins CI/CD pipelines from scratch, reducing deployment times by 40\% and improving release consistency.
        \item \textbf{Monitoring \& Observability:} Designed and implemented a comprehensive observability stack (Prometheus, Node-Exporter, cAdvisor, Loki, Grafana) with 31 custom dashboards and 72 alert rules, enabling real-time system monitoring and proactive issue resolution.
        \item \textbf{Cost Optimization:} Identified and removed underutilized servers, achieving a 25\% reduction in cloud infrastructure costs.
        \item \textbf{High-Availability Systems:} Built and managed a MariaDB Galera Cluster with HAProxy and failover capabilities, ensuring high availability and scalability for multi-node environments.
        \item \textbf{Secure Environments:} Established a secure VPN network for Development, Staging, and Production environments, enabling secure remote work for developers.
        \item \textbf{Tool Deployment:} Successfully deployed and managed critical tools including Plane (project management), AppWrite (self-hosted), Nginx, and Traefik (reverse proxies), improving team collaboration and application performance.
        \item \textbf{Scalable Infrastructure:} Managed 21 nodes and created 24 CI/CD pipelines, supporting seamless scaling of applications and services.
        \item \textbf{WordPress Optimization:} 
        \begin{itemize}
            \item Enhanced WordPress performance through horizontal scaling, reducing page load times by 30\%.
            \item Migrated file storage to object storage, improving scalability and reducing storage costs by 20\%.
        \end{itemize}
    \end{itemize}
\end{itemize}

\subsection{Gokomodo - Agricultural Supply Chain}
\subsubsection{Engineering Manager | Sep 2022 - February 2024 \hfill Jakarta, Hybrid}
\begin{itemize}
    \item \textbf{Mission:} Oversee a diverse team of over 20 members across multiple software engineering functions including Back-End, Front-End Web, Front-End Mobile, QA Manual, QA Automation, and DevOps. Successfully maintained nearly zero major incidents annually through effective management and team leadership.
    \item \textbf{Tech Stack:} Go, Docker, PostgreSQL, Redis, React, React Native, AWS, GCP
    \item \textbf{Key Achievements:}
    \begin{itemize}
        \item \textbf{DevOps Excellence:}
        \begin{itemize}
            \item Implemented cost-saving measures for cloud and infrastructure expenses, ensuring effective resource utilization.
            \item Developed self-service tools for app deployment, configuration management, and service restarts, reducing dependencies on the DevOps team.
        \end{itemize}
        \item \textbf{Quality Assurance Enhancement:}
        \begin{itemize}
            \item Standardized QA processes, including test cases, bug reports, and test plans.
            \item Advanced automation testing implementation, setting up essential tools and fostering team collaboration.
        \end{itemize}
        \item \textbf{Technical Leadership:}
        \begin{itemize}
            \item Established project templates based on clean architecture for enhanced testing and maintainability.
            \item Conducted thorough reviews of database designs and critical feature implementations.
        \end{itemize}
        \item \textbf{Team Management:}
        \begin{itemize}
            \item Streamlined interview and testing processes for new software engineers.
            \item Conducted regular one-on-one meetings and performance reviews.
            \item Initiated knowledge sharing sessions and team activities for professional growth.
        \end{itemize}
        \item \textbf{Process Improvement:}
        \begin{itemize}
            \item Standardized task breakdown methodology and Jira usage for project management.
            \item Led effective Sprint Planning and Sprint Grooming sessions.
        \end{itemize}
    \end{itemize}
\end{itemize}

\subsection{Chatat - PoS, Accounting, Web Builder}
\subsubsection{CTO | Mar 2022 - Sep 2022\hfill Jakarta, Remote}
\begin{itemize}
    \item \textbf{Tech Stack:} Go, Docker, PostgreSQL, Redis, React, React Native, AWS
    \item \textbf{Key Achievements:}
    \begin{itemize}
        \item \textbf{Strategic Leadership:}
        \begin{itemize}
            \item Outlined company's technological vision and implemented efficiency strategies.
            \item Led team in building and roadmapping profitable products.
            \item Conducted root-cause analysis to identify departmental pain points.
            \item Managed technology organization overseeing product, design, and technology teams.
        \end{itemize}
    \end{itemize}
\end{itemize}

\subsubsection{Head Of Engineering | Jul 2021 - Mar 2022 \hfill Jakarta, Remote}
\begin{itemize}
    \item \textbf{Tech Stack:} Go, Docker, PostgreSQL, Redis, React, React Native, AWS
    \item \textbf{Key Achievements:}
    \begin{itemize}
        \item \textbf{Team Leadership:}
        \begin{itemize}
            \item Led engineering department from hiring to project management.
            \item Implemented monthly one-on-one reviews and sharing sessions.
            \item Developed and implemented scrum methodology.
        \end{itemize}
        \item \textbf{Process Improvement:}
        \begin{itemize}
            \item Managed engineering projects end-to-end with focus on continuous improvement.
            \item Designed strategies for future development aligned with company objectives.
        \end{itemize}
    \end{itemize}
\end{itemize}

\subsubsection{Lead Backend Engineer | May 2021 - Jul 2021 \hfill Jakarta, Remote}
\begin{itemize}
    \item \textbf{Tech Stack:} Go, Docker, PostgreSQL, Redis, React, React Native, AWS
    \item \textbf{Key Achievements:}
    \begin{itemize}
        \item \textbf{Infrastructure Improvements:}
        \begin{itemize}
            \item Built automation for BitBucket Pipeline deployment.
            \item Created comprehensive documentation for backend codebase onboarding.
            \item Developed service architecture for simplified DevOps configuration.
        \end{itemize}
    \end{itemize}
\end{itemize}

\subsection{AVANA - Social Commerce \& Web Builder}
\subsubsection{DevOps Engineer | Jul 2021 - Nov 2021 \hfill Malaysia, Remote}
\begin{itemize}
    \item \textbf{Tech Stack:} AWS, Docker, MySQL, PHP, Laravel, Symphony, React, Serverless
    \item \textbf{Key Achievements:}
    \begin{itemize}
        \item \textbf{Infrastructure Migration:}
        \begin{itemize}
            \item Successfully migrated legacy service deployment from EC2 to Fargate.
            \item Increased system capacity from 283 RPS to 13,000+ RPS with zero downtime.
        \end{itemize}
        \item \textbf{Process Improvement:}
        \begin{itemize}
            \item Analyzed existing technology and developed comprehensive improvement plans.
            \item Established key milestones and streamlined cross-department collaboration.
            \item Supported engineers in creating and demonstrating practical solutions.
        \end{itemize}
    \end{itemize}
\end{itemize}

\subsection{Grab}
\subsubsection{SWE, Backend (Merchant Experience) | Apr 2020 - Jul 2021 \hfill Jakarta, Remote}
\begin{itemize}
    \item \textbf{Tech Stack:} Go, Docker, MySQL, Kafka, Redis, Aerospike, Jenkins, Kubernetes
    \item \textbf{Key Achievements:}
    \begin{itemize}
        \item \textbf{Platform Development:}
        \begin{itemize}
            \item Led development of merchant.grab.com from ground up to completion.
            \item Developed backend API endpoints using Go and various databases.
            \item Integrated Kafka data sources with Grab API.
            \item Designed and implemented scalable solutions using Go.
            \item Collaborated with cross-functional teams for complex feature development.
        \end{itemize}
        \item \textbf{Documentation \& Tools:}
        \begin{itemize}
            \item Created comprehensive engineering specifications and tutorials.
            \item Developed docker-compose setup for frontend team collaboration.
            \item Managed component uptime and availability through HA best practices.
            \item Conducted service capacity planning and performance optimization.
        \end{itemize}
    \end{itemize}
\end{itemize}

\subsubsection{SWE, Developer Experience (GrabKios) | Aug 2019 - Apr 2020 \hfill Jakarta, Hybrid}
\begin{itemize}
    \item \textbf{Tech Stack:} Go, Docker, MySQL, Kafka, Redis, Aerospike, Jenkins, Kubernetes, React, OpenAPI
    \item \textbf{Key Achievements:}
    \begin{itemize}
        \item \textbf{API Mocking Platform Development:}
        \begin{itemize}
            \item Architected and implemented an API mocking system to improve development efficiency:
            \begin{itemize}
                \item Built a Go-based REST API with auto-generated endpoints from OpenAPI V3 specification
                \item Developed a React web app with SSO integration for API documentation and mocking interface
                \item Implemented Jenkins CI pipeline for automated API mock updates and documentation synchronization
            \end{itemize}
            \item Significantly reduced frontend-backend development dependencies and improved sprint efficiency
        \end{itemize}
        \item \textbf{DevOps \& Infrastructure:}
        \begin{itemize}
            \item Created custom SonarQube QualityGate configurations enabling flexible code coverage requirements:
            \begin{itemize}
                \item Implemented file-specific and branch-based test coverage thresholds
                \item Facilitated legacy code maintenance while maintaining code quality standards
            \end{itemize}
            \item Developed Helm Chart generation tools to streamline Kubernetes service onboarding
            \item Optimized microservices performance and resolved scalability issues
        \end{itemize}
        \item \textbf{System Reliability:}
        \begin{itemize}
            \item Managed component uptime and availability through HA best practices
            \item Conducted service capacity planning and performance optimization
        \end{itemize}
        \item \textbf{Technical Development:}
        \begin{itemize}
            \item Designed and implemented scalable solutions using Go.
            \item Collaborated with cross-functional teams for complex feature development.
        \end{itemize}
    \end{itemize}
\end{itemize}



\subsection{Nusatek.id - IT Consultant \& Software House}
\subsubsection{Lead Backend Engineer | Feb 2019 - Aug 2019 \hfill Jakarta, On-site}
\begin{itemize}
    \item \textbf{Tech Stack:} Node.js, Express.js, Go, React, Docker, MongoDB, MySQL
    \item \textbf{Key Achievements:}
    \begin{itemize}
        \item \textbf{Full-Stack Development:}
        \begin{itemize}
            \item Created management dashboard for ManyOption (moaja.id) using React.
            \item Developed API for apartment room CSV import using Express.js \& MongoDB.
        \end{itemize}
    \end{itemize}
\end{itemize}

\subsubsection{Software Engineer | Sep 2018 - Feb 2019 \hfill Jakarta, On-site}
\begin{itemize}
    \item \textbf{Tech Stack:} Node.js, Express.js, React, MongoDB
    \item \textbf{Key Achievements:}
    \begin{itemize}
        \item \textbf{Application Development:}
        \begin{itemize}
            \item Built management dashboard frontend using React.
            \item Developed CSV import API using Express.js and MongoDB.
        \end{itemize}
    \end{itemize}
\end{itemize}

\subsection{Volantech.io - IT Consultant and Software House}
\subsubsection{SWE, Junior Backend | Sep 2018 - Feb 2019 \hfill Jakarta, Freelance}
\begin{itemize}
    \item \textbf{Tech Stack:} Node.js, MongoDB, Meteor.js, Angular.js, Angular 5
    \item \textbf{Key Achievements:}
    \begin{itemize}
        \item \textbf{Asian Para Games 2018:}
        \begin{itemize}
            \item Developed web applications and REST APIs using Node.js stack.
            \item Created interactive web interfaces using Angular frameworks.
            \item Ensured seamless integration between frontend and backend systems.
        \end{itemize}
    \end{itemize}
\end{itemize}

\subsection{Hyperpedia.id - PC Gaming Consultant and Store}
\subsubsection{Full-Stack Engineer | Mar 2018 - Sep 2018 \hfill Jakarta, Freelance}
\begin{itemize}
    \item \textbf{Tech Stack:} PHP, WordPress, Custom Plugins, Custom Themes, CSS
    \item \textbf{Key Achievements:}
    \begin{itemize}
        \item \textbf{Custom Development:}
        \begin{itemize}
            \item Created custom WordPress plugins for PC assembly interface.
            \item Designed and implemented responsive user interfaces.
            \item Developed maintainable, client-specific solutions.
        \end{itemize}
    \end{itemize}
\end{itemize}

\section{Skills}
%===============
\begin{description}
    \item[Programming Languages] Go, Node.js, TypeScript, Python, PHP, Elixir (Learning).
    \item[DevOps] Jenkins, Terraform, Ansible, Docker, Docker Compose, Docker Swarm, Kubernetes.
    \item[Datastore] MongoDB, PostgreSQL, Redis, Aerospike, MySQL.
    \item[Message Broker/Queue] Kafka, RabbitMQ, SQS.
    \item[Cloud] AWS, GCP, Azure, UpCloud, Vultr, Digital Ocean, Alibaba Cloud.
    \item[Front-End Framework] React, Remix, Next.js.
    \item[Back-End Framework] Echo, Nest.js, Express.js Laravel, Symfony.
    \item[Mobile Framework] React Native.
    \item[Language] Bahasa Indonesia, English.
    \item[Interests] Software Engineering, AI, LLM, Brazilian Jiu-Jitsu.
\end{description}

\section{Certification \& Training}
%===============================
\begin{enumerate}[itemsep=0pt]
    \item [2024] [GitHub] \href{https://www.credly.com/badges/e7f6e3ea-cd4b-4b30-b5df-9099d23649c9/public_url}{GitHub Foundations} 
    \item [2021] [Alibaba Cloud] 6th Generation Elastic Compute Service Technical Essentials
    \item [2021] [Alibaba Cloud] Relational Database Service Technical Operations
    \item [2021] [Alibaba Cloud] Cloud Computing Using OSS to Publish a Static Website
    \item [2021] [Alibaba Cloud] Using ECS to Construct a Dynamic Website
    \item [2020] [AWS] Advance Architecting on AWS
    \item [2020] [AWS] AWS Cloud Practitioner
    \item [2019] [Coursera] GCP Platform Fundamentals: Core Infrastructure by Google Cloud
    \item [2019] [Hacktiv8] Scalable Web Services with Golang Class
\end{enumerate}

\section{Education}
\vspace{0.5\baselineskip}

\subsection{Asia Cyber University $|$ {\normalfont\textit{Bachelor of Accounting}} \hfill 2024 - On Going}
\vspace{0.5\baselineskip}

\end{document}